Another paper with lots of text and fancy pictures

### 2023-09-27 paper.tex
C0.5 criterion

@@

\section{Results}
In this section we compute correlation functions along the plane $XY$ for some
real samples, namely one three-dimensional XCT and one two-dimensional SEM
sample. Table \ref{tab:summary} contains information about these samples. Images
of the samples are on \cref{fig:samples}. On the plots of correlation functions
we provide a family of curves with the first argument of the correlation
function being fixed.

>>>>

Input images must have appropriately high resolution for edge detection filter
to work correctly. A criterion for ``goodness'' of an image can be expressed
with $C_{\alpha}$ parameter \cite{samarin2023robust}. Let $\alpha \in [0, 1]$
and $f(x)$ be (band-limited) input image ($x \in \mathbb{R}^2$ or
$\mathbb{R}^3$). We define $C_\alpha$ as follows:
\begin{equation}
  \begin{aligned}
    f_0(x) &= f(x) - \langle f(x) \rangle \\
    C_\alpha &= \frac{\int_{-\alpha\omega}^{\alpha\omega} |\hat{f_0}(z)|^2
      dz}{\int_{-\omega}^{\omega} |\hat{f_0}(z)|^2 dz}
  \end{aligned}
\end{equation}
where $\hat{f_0}$ is a Fourier transform of $f_0$ and $\omega$ is a folding
frequency which depends only on resolution of the image. If a criterion
$C_{0.5} > 0.97$ holds then the image is suitable for application of
aforementioned algorithms for calculation of surface functions.

@@

\section{Results}
In this section we compute correlation functions along the plane $XY$ for some
real samples, namely one three-dimensional XCT and one two-dimensional SEM
sample. Table \ref{tab:summary} contains information about these samples. Note
that the criterion $C_{0.5} > 0.97$ holds for both of the samples. Images of the
samples are on \cref{fig:samples}. On the plots of correlation functions we
provide a family of curves with the first argument of the correlation function
being fixed.
